SCM plan for a troubling company

### 2012-01-22 article.tex
Somewhat finished

\documentclass[a4paper,11pt]{article}
\usepackage[utf8x]{inputenc}
\usepackage{cite}

@@

\subsubsection{Choices}
From the above requirements the choices are quite open. Most tools support the
branching required and the cherry-picking of changes can be made in most tools
albeit more or less easily. The distributed nature is not needed as access to
the server is good and most developers are not experienced enough to take
advantages of local commits and branches, and those that are can work that way
against the server using personal branches.

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage[utf8x]{inputenc}
\usepackage{cite}
\usepackage{url}

@@

\subsubsection{Choices}
From the above requirements the choices are quite open. Most tools support the
branching required and the cherry-picking of changes can be made in most tools
albeit more or less easily. Those that don't have it can generate patches for
the changeset and those can be applied to the desired branch. The distributed
nature is not needed as access to the server is good and most developers are not
experienced enough to take advantages of local commits and branches, and those
that are can work that way against the server using personal branches.

We will recommend using at \emph{SVN}\footnote{Subversion} \cite{SVN}. SVN is
an open source project that started with a goal of building a tool similar to
the older CVS but correcting a number of problems CVS had as in the design. It
is very mature, used extensively and supports all the features the company
needs. It also has an eclipse plugin that is very well maintained and
installable as from the standard eclipse repositories. The layout we suggest is
to keep the modules as their own projects in their own repositories and setting
up a build environment using what's called \emph{svn:externals} to create a main
project that can be used for building.
